---
title: "TreeTalkers Check ULE"
author: "Isabel Grisales"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{=tex}
\setlength\parindent{0pt}
\setlength{\parskip}{0pt}
```
```{r setup, include=F, echo = F,  fig.align="center", results="asis"}
knitr::opts_chunk$set(warning = FALSE, echo = F)
```

# 1. Summary of TT Alerts

This information is showing the alerts coming from the TreeTalkers data.

Note: The meaning of "YYYYww" is the year and week of the year from data that were assessed periodically every week.

```{r 1, message=FALSE, results="asis"}

library(ggplot2)
whichDay <- as.Date(Sys.Date())

#input_path <- file.path("C:", "out", "1")
input_files_csv <- list.files("C:/TreeTalkerDB/TTResults", full.names = T, pattern = ".csv")

# Read input files
lista_files_read <- lapply(input_files_csv, read.table, sep = ";", header = T)

angleAlert <- lista_files_read[[1]]   #
batteryAlert <- lista_files_read[[2]] #
growthAlert <- lista_files_read[[3]]  #
SFDAlert <- lista_files_read[[4]]     #
FullDB <- lista_files_read[[5]]

# TTAlerts
if(nrow(batteryAlert)==0){
cat("No issues related with the batteries where automatically identified")  
}else{
cat("The number of battery issues are", nrow(batteryAlert))
knitr::kable(batteryAlert, caption = "Issues related with batteries (mV)")
}

cat("  \n")
cat("  \n")
cat("  \n")

if(nrow(SFDAlert)==0){
cat("No issues related with the sap flux density where automatically identified")  
}else{
cat("The number of sap flux density issues are", nrow(SFDAlert))
knitr::kable(SFDAlert, caption = "Issues related with sap flux density (l d m-2 h-1)")
}

cat("  \n")
cat("  \n")
cat("  \n")

if(nrow(growthAlert)==0){
cat("No issues related with the weekly radial growth where automatically identified")  
}else{
cat("The number of weekly radial growth issues are", nrow(growthAlert))
knitr::kable(growthAlert, caption = "Issues related with the weekly radial growth (mm)")
}

cat("  \n")
cat("  \n")
cat("  \n")

if(nrow(angleAlert)==0){
cat("No issues related with the tree angles where automatically identified")  
}else{
cat("The number of tree angles issues are", nrow(angleAlert))
knitr::kable(angleAlert, caption = "Issues related with the tree angles (°)")
}

cat("  \n")
cat("  \n")
cat("  \n")

```
\newpage

# 2. TT graphs

The graphs are important to understand if the sensors are working properly and to detect the trend of the TreeTalkers batteries, air temperature, air humidity, weekly radial growth, sap flux density and the spectral bands per each tree.

## 2.1. Temperature

```{r Temperature, echo=FALSE, fig.show='asis', out.width='100%', fig.align='center', out.extra=NULL, fig.cap ="Air temperature"}

Plots_dir_list <- list.dirs("C:/TreeTalkerDB/TTPlots", recursive = FALSE)

temperaturePlots <- list.files(Plots_dir_list, pattern = "Temperature", full.names = TRUE)

knitr::include_graphics(temperaturePlots)
```
\newpage

## 2.2. Humidity

```{r Humidity, echo=FALSE, fig.show='asis', out.width='100%', fig.align='center', out.extra=NULL, fig.cap ="Air Humidity"}

HumidityPlots <- list.files(Plots_dir_list, pattern = "Humidity", full.names = TRUE)

knitr::include_graphics(HumidityPlots)
```
\newpage

## 2.3. Stem radial growth variation

```{r RadialGrowth, cho=FALSE, out.width='100%', fig.show='asis', fig.align='center', out.extra=NULL, fig.cap = "Stem radial growth variation"}

growthPlots <- list.files(Plots_dir_list, pattern = "RadialGrowth", full.names = TRUE)

knitr::include_graphics(growthPlots)
```
\newpage

## 2.4. Sap flux Density

```{r Sapflow, echo=FALSE, out.width='100%', fig.show='asis', fig.align='center', out.extra=NULL, fig.cap ="Sap flux Density"}

SapfluxDensityPlots <- list.files(Plots_dir_list, pattern = "sapFluxDensity", full.names = TRUE)

knitr::include_graphics(SapfluxDensityPlots)
```
\newpage

## 2.5. Spectral light bands through the canopy

```{r SpectralBands, echo=FALSE, out.width='100%', fig.show='asis', fig.align='center', out.extra=NULL, fig.cap ="Spectral light bands through the canopy"}

spectrometerPlots <- list.files(Plots_dir_list, pattern = "SpectralBands", full.names = TRUE)

knitr::include_graphics(spectrometerPlots)
```
\newpage

## 2.6. Stem Water Content

```{r RelStemSaturation, echo=FALSE, out.width='100%', fig.show='asis', fig.align='center', out.extra=NULL, fig.cap ="Stem Water Content"}

stwcPlots <- list.files(Plots_dir_list, pattern = "RelStemSaturation", full.names = TRUE)

knitr::include_graphics(stwcPlots)
```
\newpage

## 2.7. TreeTalkers Battery Level

```{r Battery, echo=FALSE, out.width='100%', fig.show='asis', fig.align='center', out.extra=NULL, fig.cap ="TreeTalkers Battery Level"}

batteryPlots <- list.files(Plots_dir_list, pattern = "Battery", full.names = TRUE)

knitr::include_graphics(file.path(batteryPlots))
```
